Fast and Error-Adaptive Count-Distinct Sketch \\for Influence Maximization

### 2021-01-12 paper.tex
progress

In figure \ref{fig:sketch-saturation}, we show the effect of register saturation by comparing two methods; one that uses a new sketch, that build on the residual graph after seed sets' reachability is removed,for all iterations. Other, builds the sketch once at the beginning, then only utilizes sketch merge operations to find the seed set. 
Even though at first few vertices expected influence is comparable, we see observe near-linear drop-off in estimated influence.

Since building sketches with \acro is very fast, we exploit this by rebuilding sketches after observing large cardinality estimation errors.
After adding vertices to the seed set, \acro performs Monte-Carlo simulations to estimate the reachability of the latent seed set.
The sketches are assumed as stale if the absolute error in estimated total influence score is more than the global threshold, $\epsilon_{g}$, 
and the marginal gain estimation error after the last sketch is larger than a local threshold $\epsilon_{l}$.

@@

Our method's performance, both in terms of speed and quality of results, depends on parameter selection. 
Even though,

>>>>

In figure \ref{fig:sketch-saturation}, we show the effect of register saturation by comparing two methods; one that uses a new sketch, that build on the residual graph after seed sets' reachability is removed, for all iterations. Other, builds the sketch once at the beginning, then only utilizes sketch merge operations to find the seed set. 
Even though at first few vertices expected influence is comparable, we see observe near-linear drop-off in estimated influence.

Since building sketches with \acro is very fast, we exploit this by rebuilding sketches after observing large cardinality estimation errors.
After adding vertices to the seed set, \acro performs Monte-Carlo simulations to estimate the reachability of the latent seed set.
The sketches are assumed as stale if the absolute error in estimated total influence score is more than the global threshold, $\epsilon_{global}$, 
and the marginal gain estimation error after the last sketch is larger than a local threshold $\epsilon_{local}$.

@@

Even though, \acro's behavior is not chaotic with respect to changes in parameters. Our method's performance, both in terms of speed and quality of results, depends on parameter selection. Setting $\epsilon_local$ to $0$ means that \acro will always rebuild sketches, which would slowdown the method but it will give the best possible results. On the other hand, setting $\epsilon_local$ to infinity will be very fast, since sketches are build only once without checking vertices blocked. But, quality of the results will suffer.
